---
title: "data_pre_processing"
author: "Dongyuan Song"
date: "2018/12/2"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
  github_document: default
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, 
                      #root.dir = "/n/irizarryfs01_backed_up/songdongyuan/PBM-Exploration/", 
                      root.dir = "D:/MS/Master Course/BST260/BST260/", 
                      fig.width = 8, fig.height = 6)
```

```{r}
library(tidyverse)
```


## Data Pre-processing

This is the begining file for data pre-processing.

### Clean original csv manually

A63, A75, A106  
BI4, BI5, BI69

### Read in csv and modify it
```{r}
dat <- read_csv("./data/food_coded_clean.csv", na = "nan")
```

```{r}
head(dat)
```

We notice that here is some duplicated columns. Filter out those columns.
```{r}
dat <- dat %>% dplyr::select( - ends_with("_1"))
```

```{r}
head(dat)
```

Convert `int` to `factor` as most of them are categorical data.
```{r}
dat <- dat %>% dplyr::mutate_if(is.integer, as.factor)
```

```{r}
head(dat)
```

However, there are some oridinary categorical data. We convert them them back to numeric data.
11.Cook, 19.Eating out, 21.Ethnic food, 22 Exercise, 23 Father Education, 30 Fruit day, 
30.grade level, 32.Greek Food, 37.Income, 38.Indian Food, 39.Italian Food, 43.mothers education,
45.nutritional_check, 46 parents_cook, 48) pay_meal_out, 49) Persian_food, 53) Tai_food 57) veggies_day,

```{r}
dat <- dat %>% dplyr::mutate_at(vars(ends_with("_food")), as.integer)
```

```{r}
dat <- dat %>% dplyr::mutate_at(vars(ends_with("_education")), as.integer)
```

```{r}
dat <- dat %>% dplyr::mutate_at(vars(ends_with("_day")), as.integer)
```

```{r}
dat <- dat %>% dplyr::mutate_at(.funs = as.integer, .vars = c("cook", 
                                                             "eating_out", "exercise", "grade_level",
                                                             "income", "nutritional_check", 
                                                             "parents_cook", "pay_meal_out"))
```

```{r}
dat <- dat %>% dplyr::mutate(fav_food = as.factor(fav_food))
```


```{r}
head(dat)
```

Save rds
```{r}
saveRDS(dat, "./data/breakfast_clean.rds")
```

